Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-09-22 packages/spec-haskell/yellowpaper/Paper.tex
subsection FILLED: payment primitives

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Document Preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper]{report}

@@

\section{Payment System}

@@

\subsection{Money Distribution Models}

@@

\begin{itemize}
\item If time is included the shared context, then monetary value of each money unit can be continuous over time.
\item A subset of money units can also have their value functions depending on the same information in shared
    context. This could enable payment primitives that involve many parties.
\end{itemize}

@@

\input{MoneyDistributionConcepts.tex}

\subsection{Payment Primitives}

\subsection{Payment System Models}

\subsubsection{Discrete Payments}

\subsubsection{Continuous Payments}

\subsection{Money Medium Models}

@@

\section{Relevant Approaches}

\subsection{Constraint Programming}

\subsection{Functional Reactive Programming}

\subsection{Denotational Semantics}

@@

\section{Denotational Semantics}

@@

\subsection{Monoidial Payment Model}

@@

\subsection{Payment Premitives}

@@

\section{Restatement in Haskell}

@@

\section{Type Of Money Units}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Document Preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,10pt]{report}

%% \usepackage[margin=0.5in,nomarginpar]{geometry}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\section{Payment System}
%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Money Distribution Models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
\item If time is included the shared context, then monetary value of each monetary unit can be continuous over time.
\item A subset of monetary units can also have their value functions depending on the same information in shared
    context. This could enable payment primitives that involve many parties.
\end{itemize}

@@

\input{MoneyDistribution.lhs.tex}

\subsection{Payment Primitives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Payment primitives are functions that takes a money distribution, shared context and some arbitrary arguments as inputs
and an updated money distribution and shared context as outputs:

\begin{minted}[escapeinside=||,mathescape=true]{haskell}
    somePaymentPrimitive :: MoneyDistribution |$\otimes$| SharedContext
                         -> Args
                         -> MoneyDistribution |$\otimes$| SharedContext
\end{minted}

Loosely speaking, it is considered a primitive, if it can not be broken down into other existing primitives which result
in the same money distribution.

The best known primitive is instant transfer of monetary value between one monetary unit to another. Shared context
enables more primitives to be defined, which will be introduced in later chapters.

\subsection{Payment System Models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Discrete Payments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Continuous Payments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Money Medium Models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relevant Approaches}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Constraint Programming}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Functional Reactive Programming}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Denotational Semantics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Denotational Semantics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Monoidial Payment Model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Payment Primitives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Restatement in Haskell}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Type Of Monetary Units}
